\documentclass[11pt]{article}

\usepackage{fancyhdr} % Required for custom headers
\usepackage[explicit]{titlesec}
\usepackage{extramarks} % Required for headers and footers
\usepackage[usenames,dvipsnames]{color} % Required for custom colors
\usepackage{graphicx} % Required to insert images
\usepackage{listings} % Required for insertion of code
%\usepackage{courier} % Required for the courier font
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1} % Line spacing

% Set up the header
\pagestyle{fancy}
\lhead{\hmwkAuthorName} % Top left header
\chead{\hmwkClass\ : \hmwkTitle} % Top center head
\rhead{\firstxmark} % Top right header
\renewcommand\headrulewidth{0.4pt} % Size of the header rule

\setlength\parindent{0pt} % Removes all indentation from paragraphs


\newcommand{\hmwkTitle}{Final Project Proposal} % Assignment title
\newcommand{\hmwkClass}{Cis\ 192} % Course/class
\newcommand{\hmwkAuthorName}{Boris Treskunov} % Your name

\begin{document}
\pagenumbering{gobble}
\section*{Project Idea}

I would like to create a website that allows users at Penn to coordinate cab rides with one another: \textbf{PennCab}. A good usage example is for cabs to and from the airport: let's say after Winter Break you have a flight back to Philadelphia that lands at, say, 9:00pm and you don't want to pay the \$30+ for a cab by yourself. You can create a cab ride on the website that others (anyone at Penn) can join, and then you can share the ride back together!

\section*{Goals}

\begin{enumerate}
\item Users should be able to create ``cab rides" with the following constraints:
    \begin{enumerate}
    \item Maximum number of people (defaulted to 4)
    \item Origin
    \item Destination
    \item Date
    \item Approximate departure time
    \item Optional: Event/Purpose
    \end{enumerate}

\item Users should be able to join any cab that is under capacity and in the future.
\item After users have signed up to take a cab together, their contact information will be shared amongst each other so that they can coordinate properly.
\item Sign-ups only allowed with upenn.edu email address.
\item Front-end will probably be built using a front-end framework (such as Bootstrap or Foundation) so that the focus on the project can be backend functionality in Python.

\end{enumerate}

\subsection*{Stretch/Time-Permitting Goals}
\begin{enumerate}
\item Share links to cab rides on social networks (namely, Facebook and Twitter).
\item Be able to distinguish and create both public and private cab rides. Private cab rides could be used to coordinate with friends, for example.
\item Better way of ensuring only Penn students can sign up for website (e-mail verification?).
\item TBD!
\end{enumerate}

\section*{Expected Python Package Usage}

The main packages I will be using are Flask or Django, and a database package (probably MySQLdb or PyMongo).

\section*{Team Members and Divison of Labor}

Just me!

\end{document}